Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-17 ms.qmd
Fixes

@@

# Lets explore the model and how it's predciting the real data
  data_w_pred <- cbind(lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),], predict(model5_bayes))

@@

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds). Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

@@

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false

if(rerun){
  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

>>>>

# Populations and species?
pop_spp_w <- climate2[complete.cases(climate2),]

@@

# Lets explore the model and how it's predciting the real data
  data_w <- lnCVRQ10_data_wild[complete.cases(lnCVRQ10_data_wild$c_accl_time),]

# combine with predictions
  data_w_pred <- cbind(data_w, predict(model5_bayes))

@@

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(pop_spp_w$Species))`, from `r dim(pop_spp_w)[1]` populations). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds). Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

@@

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false
rerun = FALSE
if(rerun){
  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)
